Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
Related work 2,3 updated.

In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements. They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths. Their are three predict targets: $(i)$ the remaining life time of a route (i.e., the time before a route changes), $(ii)$ the number of route changes in a future timeslot, and $(iii)$ the average RTT  that the path $P$ will experience in the next \texttt{traceroute} measurement.

@@

1. introduce the original paper

In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a route for one path at time $t$ (i.e., the time before a route changes), namely $R_r(t)$, $(ii)$ the number of route changes for one path $P$ in a future timeslot $T$, namely $rcP_T$  and $(iii)$ the average RTT that the path $P$ will experience in the next \texttt{traceroute} measurement, namely $avgRTT_P(t)$.

@@

2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}

@@

\section{Methodology}
\subsection{Data Processing}
We reprocess the data in several more rational ways, which in other words, predicting targets using the previous information only. And to be specific, we divide the data into two sets, namely training set and test set. We calculate statistical properties (global features) of paths using three different methods: $(i)$ use the global features (max, min, average, percentiles, etc.) in the training set to get the model and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global feature of the former $k\%$ to train the models and update these features during the predicting procedure(i.e.,update the global features everytime there is a new \texttt{traceroute} measurement of a path), and $(iii)$ only use recent \texttt{traceroute} data of certain length (namely $window\ size$) in the training set to calculate the global features, and when using the trained model to predict targets, we only consider features calculated in  recent \texttt{traceroute} measurements of the same $window\ size$ . For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th method ($i$ can be either 1,2 or 3). And for the third method, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.

@@

\section{Experiment}
\subsection{Random Forest Model}
In our experiment, firstly, we use the standard random forest model (the same as the original paper) with the reprocessed data.  In practice, we set $k = 70, 80$ respectively. And in the third method of processing data, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively. We find that there is little difference when setting $k$ either to 70 or 80. Below are the results when $k = 70$. And we also define an evaluation metric $ABC$, which indicates the  area below the curve ($ABC\in[0,1]$). The closer $ABC$ is to $1$, the better prediction result it has. These figures in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} and  illustrate the relationship between sample percentage and relative prediction error(i.e., $\mid Real - Predict\mid/ Real $). 
\begin{figure*} [!htb] 
	%\vspace{-4pt}  
	\centering  
	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-RF.jpg}  
	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-RF.jpg} 
\end{figure*} 
\begin{figure*} 	
	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize10-RF.jpg} 
	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize20-RF.jpg}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize50-RF.jpg}
	%\vspace{-20pt}  
	\caption{Relative prediction errors for $R_r(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
	\label{fig:task1_RF}  
	%\vspace{-10pt}  
\end{figure*}

\begin{figure*} [!htb] 
	%\vspace{-4pt}  
	\centering  
	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-RF.jpg}  
	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-RF.jpg} 
\end{figure*} 
\begin{figure*} 	
	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize10-RF.jpg} 
	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize20-RF.jpg}
	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize50-RF.jpg}
	%\vspace{-20pt}  
	\caption{Relative prediction errors for $avgRTT_P(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
	\label{fig:task3_RF}
	%\vspace{-10pt}  
\end{figure*}

Table 1 describes the $ABC$ in each figure.
\begin{table}[tbp]
	\centering  % 表居中
	\begin{tabular}{lcc} 
		\hline
		Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
		$data-1$ & 0.4016    &0.8124   \\        
		$data-2$ &0.3985 &0.8261 \\        
		$data-3-ws10$  &0.7132 &0.8018 \\
		$data-3-ws20$ &0.6314 &0.7910 \\
		$data-3-ws50$ &0.5359  &0.7790 \\ \hline
	\end{tabular}
	\caption{The $ABC$ of curves
		 in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} }
	 \label{tab:result_RF}
\end{table}
From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different methods to process the data. They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality. However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality. It changes rapidly as time changes. And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model. Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing methods. It considers only the recent data in a relatively short time slot. Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the previous \texttt{traceroute} data).
\subsection{Deep Models}

@@

	\section{Related Works}
	1. introduce the original paper
	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

@@

	2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}

>>>>

@@

\paragraph{The Original Paper}

In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

@@

\paragraph{Other Applications of MLCN}
The last 2 decades has seen emerging applications of machine learning techniques used in computer networks \cite{kwon2017survey}. Classic methods, such as SVM, RBM, PCA and LDA, and deep learning methods including DBN, DNN and RNN, are both applied to areas like anomaly detection, web security, traffic prediction, etc. A usual procedure is to use autoencoders, both deep and classic ones, for dimensionality reduction and depend on SVM and DBN as a classifier.

Here we mention a few representative works. Alom et al. \cite{alom2015intrusion} focus on intrusion detection system. Tao et al. \cite{tao2016big} search to build a data fusion algorithm with awareness of network security situation obtained by PCA, LDA and Fisher score. Lv et al. \cite{lv2015traffic} first develop deep learning methods in traffic flow prediction. Hou et al. \cite{hou2010malicious} aims to learn filtering rules for malicious contents automatically. Thottan et al.~\cite{thottan2003anomaly} are among the first to introduce self-learning methods to anomaly detection and a series of botnet detection methods follows up \cite{ranjan2014machine, singh2014big, beigi2014towards, zhao2013botnet}.

\paragraph{XGBoost} XGBoost collects a series of machine learning algorithms under the Gradient Boosting framework. Specifically, we use the random forest library it provides, namely GBDT, as the implementation in the experiments. This library includes automatic hyper-parameter tuning, which saves us some labor.

\paragraph{LSTM} LSTM is an improved version of the original RNN, which largely resolved the problem of gradient vanishing and explosion in original RNN and is capable of capturing multi-scale dependencies in sequential data. The main modification it made to the original RNN unit is to add multiplicative \textbf{gate} unit that control the proportions of information to forget/pass on to the next time step. Even more modern version of LSTM like BLSTM equip the model with the ability to learn from the future, but here we only use the basic LSTM to explore the time dependencies in the dataset.

@@

\section{Methodology}
\subsection{Data Processing}

@@

\section{Experiment}
\subsection{Classic Models}
We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}. We need to find some difference between our 3 data processing methods and the authors', i.e.,\textbf{origin}.

@@

	\section{Related Works}
	\subsection{the original paper}
	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.

@@

	2. Other Applcations
